Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-05-18 tex/manuscript.tex
conclusions section

>>>>

\section*{Conclusions}
	Through addition of four herein described species, the entimine [non-focal] genus \textit{Minyomerus} [JF2018] is expanded to include 21 species.
	We predict that additional undescribed species of \textit{Minyomerus} [JF2018] exist throughout the North American deserts, given the narrow endemicity patterns of many members of the genus.
	Furthermore, we believe that sampling in poorly-sampled locales, particularly in the northwestern United States and in northern Mexico, will yield new evolutionary insights for this group.
	New molecular data can strengthen phylogenetic hypotheses and provide estimates regarding the timing of diversification of \textit{Minyomerus} [JF2018], thereby testing our current inference of an origin in central Mexico.
	Another research direction should focus on the reproductive behavior of certain species suspected to be parthenogenetic; including rearing and karyotyping.
	Finally, the validity of the genus \textit{Minyomerus} [JF2018] as a member of the Tanymecini [non-focal], and its relationships to other Entiminae [non-focal], remain uncertain.
